---
title: "How to define area"
author: "Thihung"
date: "2025-05-19"
output: html_document
---

This is the method to extract the region

Loading some necessary packages



```{r}
library(readxl)
library(readr)
library(dplyr) 
library(stringr)
library(janitor)
library(tidyverse)

```


Import and clean region sheet

```{r}
region_data <- read_excel("D:/PhD projects/health insurance database format/NHIS data/Data practices/Detailed_definition_area.xlsx", sheet = "코드설명_동읍면") %>% 
  select(SIDO_SGG_CD, SGG_NM, SIDO_NM)  %>%  # keep relevant columns
  arrange(SIDO_SGG_CD) %>%
  distinct(SIDO_SGG_CD, .keep_all = TRUE)
head(region_data)

```


Import the BNC table and merge with region_data to get the information of region.
Normaly the definition of region according to first 2 number of postcode: RVSN_ADDR_CD or SIDO_SGG_CD:
Example: 11: Seoul 


```{r}
region_code <- read_delim("D:/PhD projects/health insurance database format/NHIS data/Data practices/TXT/nsc2_edu_inst.txt") %>% 
  select(SGG_INST)

region_old <- region_code %>%
  mutate(SGG_INST = as.character(SGG_INST)) %>%
  mutate(region_old = if_else(substr(SGG_INST, 1, 2) %in% c('11','26','27','28','29','30','31','36'),
                              'urban', 'rural')) %>%count(region_old)
print(region_old)
```

Underestimate region
```{r}
check <- region_data %>% 
  filter(!substr(SIDO_SGG_CD,1,2) %in% c('11','26','27','28','29','30','31','36') &
  str_detect(SGG_NM, "구|동|시"))
head(check)  

```
Redefine region variable based on SGG_NM content
Futher edit the region old:
when area_full is rural then check the SGG_NM:
if SGG_NM contain "구|동|시" then it is not rural --> it is city



```{r}
region_new <- region_code %>%
  mutate(SGG_INST = as.character(SGG_INST)) %>%  # Convert to character
  inner_join(region_data %>% select(SIDO_SGG_CD, SGG_NM, SIDO_NM), 
             by = c("SGG_INST" = "SIDO_SGG_CD")) %>% 
  mutate(
    region_old = if_else(substr(SGG_INST, 1, 2) %in% c('11','26','27','28','29','30','31','36'),
                              'urban', 'rural'),
    area_detail = if_else(str_detect(SGG_NM, "구|동|시") | str_detect(SIDO_NM, "구|동|시"), 'urban', 'rural'),
    region_new = if_else(region_old == 'urban' | area_detail == 'urban', 'urban', 'rural')
  ) %>% count(region_new)
print(region_new)

```






